---
title: "Visualization Tool for Grades in UBCO"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

<style>
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(shiny)
library(htmlwidgets)
library(htmltools)
library(reshape2)
library(dplyr)
library (scales)

###
#Initialization of list
#setwd("C:/Users/bjcfa/Desktop/ShinyforGrade")
data_loc <- "./data"
list <- list.files("./data")
data <- list()

per <- c("Withdrew" ,"Audit" ,"Other","X.50","X50.54","X55.59"    ,"X60.63" ,   "X64.67" ,   "X68.71"  ,  "X72.75"  ,  "X76.79" ,  "X80.84"  ,  "X85.89"  ,  "X90.100")
new_per <- c("Others", "<50", "50~59", "60~71", "72~79", "80~89","90~100")
###


merge_per <- function(x){
        x <- data.frame(x)
        gg <- data.frame()
        Professor <- x$Professor
        Others <- x$Withdrew + x$Audit+ x$Other
        `<50` <- x$X.50
        `50~59` <- x$X50.54 + x$X55.59
        `60~71` <- x$X60.63 + x$X64.67 + x$X68.71 
        `72~79` <- x$X72.75 + x$X76.79 
        `80~89` <- x$X80.84 + x$X85.89 
        `90~100` <- x$X90.100
        
        
        return(data.frame(Professor,Others,`<50`, `50~59`, `60~71`, `72~79`, `80~89`,`90~100`))
}



init <- function(soci){

        soci$Course <- as.factor(soci$Course)
        soci <- soci[!soci$Section %in% "OVERALL",]
        soci$Professor <- factor(soci$Professor)
        return(soci)
        
}

init_overall <- function(soci){

        soci$Course <- as.factor(soci$Course)
        soci <- soci[soci$Section %in% "OVERALL",]
        soci$Professor <- factor(soci$Professor)
        return(soci)
        
}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
        library(grid)
        
        # Make a list from the ... arguments and plotlist
        plots <- c(list(...), plotlist)
        
        numPlots = length(plots)
        
        # If layout is NULL, then use 'cols' to determine layout
        if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
        }
        
        if (numPlots==1) {
                print(plots[[1]])
                
        } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
                
                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                        # Get the i,j matrix positions of the regions that contain this subplot
                        matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
                        
                        print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                        layout.pos.col = matchidx$col))
                }
        }
}




#for(i in list){
#        data[[i]] <- init(read.csv(paste(data_loc,"/",i,sep = "")))
#}

```


Selections {.sidebar}
===============================

Please select the subject that you want.

```{r}
## The shiny part
inputPanel(
        selectInput("subject", label = "Subject", 
             list))
activeDataset <- reactive({
   return(init(read.csv(paste(data_loc,"/",input$subject,sep = ""))))

        
})

activeDataset_overall <- reactive({
   return(init_overall(read.csv(paste(data_loc,"/",input$subject,sep = ""))))

        
})

get_course_list <- reactive({
           temp <- activeDataset()
           return(temp[,"Course"])
})

renderUI({
        selectInput("Course", "Select the course number", get_course_list() )
})





```

Overall Distribution:

Others: Studens who are condition of withdrawing, audits. X.50: less than 50. X90.100: Between 90 and 100. 
There will be error message if you didn't select any course number.

Grade Distribution by Professor:

The format is name of professor_section in overall distribution.


This website is licensed by INTELLIGENT SENSING, DIAGNOSTIC AND PROGNOSTIC RESEARCH LAB (ISDPRL) in University of British Columbia. All the commercial usages are prohibited without informing the Author. 

Author: Bin



Tables
===================================== 


Row 1 
------------------------------------
### Summary for Individual Professor

```{r}
DT::renderDataTable({
        #t_m <- init(read.csv(paste(data_loc,"/",input$subject,sep = "")))
        t_m <- activeDataset()
        t_m <- t_m[t_m$Course %in% input$Course,]
        t_m <- t_m[,c("Subject","Course","Section","Title","Professor", "Avg","High","Low", "Std.dev")]
        DT::datatable(t_m, rownames = FALSE,options = list(scrollX = TRUE,pageLength = 5,lengthMenu = c(5, 8)))
})


```

### Overall Distribution 

```{r,error=FALSE}

renderPlot({
t_m <- activeDataset_overall()
t_m <- t_m[t_m$Course %in% input$Course,]
t_m$Professor <- paste(t_m$Professor, t_m$Section, sep = "_")
title <- t_m[1,c("Subject","Course")]
temp_title <- paste(title[1,1],title[1,2],sep = "")
t_m <- t_m[,c("Professor", per)]
t_m <- merge_per(t_m)

mdf <- melt(t_m, id = "Professor")
total <- sum(mdf$value)
mdf$value <- mdf$value/total
#mdf$pos <- cumsum(mdf$value) - mdf$value/2



p <- ggplot(mdf,aes(x = factor(1),y = value, fill = variable)) + geom_bar(stat="identity", color='black')
p <- p + coord_polar(theta = 'y') + guides(fill=guide_legend(override.aes=list(colour=NA))) + theme(axis.ticks=element_blank(),  # the axis ticks
          axis.title=element_blank(),  # the axis labels
          axis.text.y=element_blank()) + scale_fill_discrete(name="Range") # the 0.75, 1.00, 1.25 labels.



p

#p <- list()
# for(i in 1:nrow(t_m)){
#         mdf <- melt(t_m[1,], id = "Professor")
#         p[[i]] <- ggplot(mdf, aes(x = factor(1), fill = factor(value))) +geom_bar(width = 1)+coord_polar(theta = "y")
# }
# ggpie <- function (dat, by, totals) {
#     ggplot(dat, aes_string(x=factor(1), y=totals, fill=by)) +
#         geom_bar(stat='identity', color='black') +
#         guides(fill=guide_legend(override.aes=list(colour=NA))) + # removes black borders from legend
#         coord_polar(theta='y') +
#         theme(axis.ticks=element_blank(),
#             axis.text.y=element_blank(),
#             axis.text.x=element_text(colour='black'),
#             axis.title=element_blank()) #+
#     + scale_y_continuous(breaks=cumsum(dat[[totals]]) - dat[[totals]] / 2, labels=dat[[by]])
# }

# library(grid)
# ggpie(mdf, by='variable', totals='value')+
#     theme(axis.ticks.margin=unit(0,"lines"),
#           plot.margin=rep(unit(0, "lines"),4))

})

```







<!-- ### Summary  -->
<!-- Summary for All Sections -->

<!-- ```{r} -->
<!-- DT::renderDataTable({ -->
<!--         #t_m <- init(read.csv(paste(data_loc,"/",input$subject,sep = ""))) -->
<!--         t_m <- activeDataset_overall() -->
<!--         t_m <- t_m[t_m$Course %in% input$Course,] -->
<!--         t_m <- t_m[,c("Subject","Course","Title","Section", "Avg","High","Low", "Std.dev")] -->
<!--         DT::datatable(t_m, rownames = FALSE,options = list(scrollX = TRUE,pageLength = 5,lengthMenu = c(5, 8))) -->
<!-- }) -->


<!-- ``` -->

Row 2 {data-width=400}
-------------------------------------


###Grade Distribution by Professor 

```{r}
renderPlot({
        
t_m <- activeDataset()
t_m <- t_m[t_m$Course %in% input$Course,]
t_m$Professor <- paste(t_m$Professor, t_m$Section, sep = "_")
title <- t_m[1,c("Subject","Course")]
temp_title <- paste(title[1,1],title[1,2],sep = "")
t_m <- t_m[,c("Professor","Avg","High","Low")]
mdf <- melt(t_m, id = "Professor")

p <- ggplot(data=mdf, aes(x=Professor, y=value, fill=variable, group = variable)) + geom_bar(stat="identity",position=position_dodge())  + theme(axis.text = element_text(size = 15), axis.title = element_text(size = 15), legend.text = element_text(size = 10), legend.position = "top") + labs( x = "Professors", y = "Grades") +guides(fill=guide_legend(title=NULL)) + coord_cartesian(ylim = c(0, 105)) + scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

p
        
})


```
